Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-09-16 ms.Rnw
Document is now fully dynamic

<<Load Model Parameters, echo=FALSE, results='hide'>>=
load('model3/output/PanelLocalAll_PF.rda')  # Final model 3 evaluations
load('model3/output/PanelLocalAll.rda')  # Final model 3 parameters (MIF search)
ll_mod3 <- mif_logLik
MIF_mod3 <- local_MIF2_search
rm(mif_logLik, local_MIF2_search, tLocal)

@@

best_m3 <- ll_mod3 %>%
  arrange(-logLik) %>%
  slice_head(n = 1) %>%
  pull(which)

p3 <- coef(MIF_mod3[[best_m3]])
rm(MIF_mod3)
gc()

@@

<<Table 2 Input, echo=FALSE, eval=TRUE>>=
NREPS_EVAL <- switch(RUN_LEVEL,  3,   8,    36)
NP_EVAL    <- switch(RUN_LEVEL, 50, 500, 10000)

@@

# Load pre-calculated model 3 likelihood
mod3_ll <- ll_mod3 %>%
  arrange(-logLik) %>%
  slice_head(n = 1) %>%
  pull(logLik)

@@

      # Perform block-particle filter
      h3_bpf <- foreach(i = 1:NREPS_EVAL, .combine = c) %dopar% {
        bpfilter(h3Spat, Np = NP_EVAL, block_size = 1)
      }

>>>>

<<FitModel3, echo=FALSE, include=FALSE, message=FALSE>>=
set.seed(636813)

if (RUN_LEVEL == 1){

  # Global search, All params
  SEARCH1 <- list(
    NP = 50, NMIF = 3, NREPS = 3,
    NREPS_EVAL = 3, NP_EVAL = 100
  )

  # Local search, unit specific params
  SEARCH2 <- list(
    TOP_N = 1, NP = 50, NMIF = 3, NREPS = 3, NREPS_EVAL = 3,
    NP_EVAL = 100
  )

  # Number of searches
  N_SEARCHES <- 2L

  # THESE SEARCHES AREN'T CONDUCTED
  SEARCH3 <- list(
    TOP_N = 1, NP = 20, NMIF = 3, NREPS = 3, NREPS_EVAL = 3, NP_EVAL = 25
  )

  SEARCH4 <- list(
    TOP_N = 1, NP = 20, NMIF = 3, NREPS = 3, NREPS_EVAL = 3, NP_EVAL = 25
  )

  SEARCH5 <- list(
    TOP_N = 1, NP = 20, NMIF = 3, NREPS = 3, NREPS_EVAL = 3, NP_EVAL = 25
  )
} else if (RUN_LEVEL == 2) {

  # Global search, all parameters
  SEARCH1 <- list(
    NP = 200, NMIF = 10, NREPS = 36, NREPS_EVAL = 36, NP_EVAL = 500
  )

  # Local search, unit specific
  SEARCH2 <- list(
    TOP_N = 2, NP = 200, NMIF = 20, NREPS = 18, NREPS_EVAL = 36, NP_EVAL = 500
  )

  # Local search, shared parameters
  SEARCH3 <- list(
    TOP_N = 2, NP = 200, NMIF = 10, NREPS = 18, NREPS_EVAL = 36, NP_EVAL = 500
  )

  # Local search, unit specific
  SEARCH4 <- list(
    TOP_N = 2, NP = 200, NMIF = 10, NREPS = 18, NREPS_EVAL = 36, NP_EVAL = 500
  )

  # Local search, all parameters
  SEARCH5 <- list(
    TOP_N = 2, NP = 200, NMIF =  5, NREPS = 18, NREPS_EVAL = 36, NP_EVAL = 500
  )

  # Number of searches
  N_SEARCHES <- 5L
} else if (RUN_LEVEL == 3) {

  # Global search, all parameters
  SEARCH1 <- list(
    NP = 1500, NMIF = 100, NREPS = 144, NREPS_EVAL = 36, NP_EVAL = 2000
  )

  # Local search, unit specific parameters
  SEARCH2 <- list(
    TOP_N = 4, NP = 2000, NMIF = 100, NREPS = 18, NREPS_EVAL = 36, NP_EVAL = 4000
  )

  # Local search, shared parameters
  SEARCH3 <- list(
    TOP_N = 3, NP = 4000, NMIF = 50, NREPS = 24, NREPS_EVAL = 36, NP_EVAL = 5000
  )

  # Local search, unit specific parameters
  SEARCH4 <- list(
    TOP_N = 3, NP = 4000, NMIF = 50, NREPS = 24, NREPS_EVAL = 36, NP_EVAL = 5000
  )

  # Local search, all parameters
  SEARCH5 <- list(
    TOP_N = 3, NP = 4000, NMIF = 25, NREPS = 24, NREPS_EVAL = 36, NP_EVAL = 5000
  )

  # Total number of searches
  N_SEARCHES <- 5L
} else {
  stop("Run level must be 1, 2 or 3.")
}

haiti3_fit <- bake(
  file = paste0("model3/", rl_dir, "haiti3_fit.rds"), {
    fit_haiti3(
      search1 = SEARCH1,
      search2 = SEARCH2,
      search3 = SEARCH3,
      search4 = SEARCH4,
      search5 = SEARCH5,
      n_searches = N_SEARCHES,
      ncores = cores
    )
  }
)

rm(SEARCH1, SEARCH2, SEARCH3, SEARCH4, SEARCH5, N_SEARCHES)
gc()
@

<<Load Model Parameters, echo=FALSE, results='hide'>>=
# load('model3/output/PanelLocalAll_PF.rda')  # Final model 3 evaluations
# load('model3/output/PanelLocalAll.rda')  # Final model 3 parameters (MIF search)

# haiti3_fit contains ll estimate for many parameter sets, so we want to find
# the highest value
mod3_ll <- max(
  haiti3_fit[[length(haiti3_fit)]]$logLiks[, 'logLik'],
  na.rm = TRUE
)

# MIF_mod3 <- local_MIF2_search
# rm(mif_logLik, local_MIF2_search, tLocal)

@@

# best_m3 <- ll_mod3 %>%
#   arrange(-logLik) %>%
#   slice_head(n = 1) %>%
#   pull(which)

best_m3 <- haiti3_fit[[length(haiti3_fit)]]$logLiks %>%
  filter(logLik == max(logLik, na.rm = TRUE)) %>%
  pull(which)

p3 <- haiti3_fit[[length(haiti3_fit)]]$params[best_m3, ]
gc()

@@

<<Table 2 Input, echo=FALSE, eval=TRUE>>=
NREPS_EVAL <- switch(RUN_LEVEL,   3,   8,    36)
NP_EVAL    <- switch(RUN_LEVEL, 100, 500, 10000)

@@

# Load pre-calculated model 3 likelihood
# mod3_ll <- ll_mod3 %>%
#   arrange(-logLik) %>%
#   slice_head(n = 1) %>%
#   pull(logLik)

@@

      # Perform block-particle filter
      h3_bpf <- foreach(i = 1:NREPS_EVAL, .combine = c) %dopar% {
        bpfilter(h3Spat, Np = NP_EVAL, block_size = 1,
                 params = haitipkg:::panelParms_toSpatParms3(p3))
      }
